TBD

### 2016-10-06 paper.tex
started adding Jacobian and Hessian

\newcommand{\bz}{\bmath{z}}
\newcommand{\bA}{\bmath{A}}
\newcommand{\br}{\bmath{r}}
\newcommand{\bg}{\bmath{g}}
\newcommand{\bd}{\bmath{d}}
\newcommand{\bv}{\bmath{v}}
\newcommand{\bn}{\bmath{n}}
\newcommand{\by}{\bmath{y}}
\newcommand{\bJ}{\bmath{J}}
\newcommand{\bD}{\bmath{D}}
\newcommand{\bN}{\bmath{N}}
\newcommand{\bM}{\bmath{M}}
\newcommand{\conj}[1]{\overline{#1}}

@@

\section{Least Squares}
Redundant calibration can be achieved by solving the following optimization problem
\begin{equation}
\label{eq:red_least_squares}
\min_{\bz} \|\bd - \bv(\bz)\|, 
\end{equation}
where $\bz = [\bg,\by]^T$. Eq.~\eqref{eq:red_least_squares} is a nonlinear least squares problem.

@@

\citet{Smirnov2015} recently proposed to use this Wirtinger framework instead of the classic real and imaginary approach to perform normal calibration. We will now show
that the Wirtinger framework can also be applied to redundant calibration. Analogous to \cite{Smirnov2015}, we recast Eq.~\eqref{eq:red_least_squares} to 
\begin{equation}
\label{eq:red_least_squares_complex}
\min_{\breve{\bz}} \|\breve{\bd} - \breve{\bv}(\breve{\bz})\|, 
\end{equation}
where $\breve{\bz} = [\bz,\conj{\bz}]^T$, $\breve{\bd} = [\bd,\conj{\bd}]^T$, $\breve{\bv} = [\bv,\conj{\bv}]$. Eq.~\eqref{eq:red_least_squares_complex} is the augmented counterpart of Eq.~\eqref{eq:red_least_squares}.
If we use the Wirtinger derivative instead of the classic notion of a derivative to define the gradient operator then 
$\bv$ becomes analytic in $\bz$ and $\conj{\bz}$ as a whole \citep{Smirnov2015}. The fact that $\breve{\bv}$ is now analytic in its argument has the immediate consequence that we can use the complex variants of the Gauss-Newton
and the Levenberg-Marquardt algorithm to solve Eq.~\eqref{eq:red_least_squares_complex}.

>>>>

\newcommand{\bz}{\bmath{z}}
\newcommand{\bA}{\bmath{A}}
\newcommand{\br}{\bmath{r}}
\newcommand{\bg}{\bmath{g}}
\newcommand{\bd}{\bmath{d}}
\newcommand{\bv}{\bmath{v}}
\newcommand{\bn}{\bmath{n}}
\newcommand{\by}{\bmath{y}}
\newcommand{\bJ}{\bmath{J}}
\newcommand{\bD}{\bmath{D}}
\newcommand{\bN}{\bmath{N}}
\newcommand{\bM}{\bmath{M}}
\newcommand{\bI}{\bmath{I}}
\newcommand{\bzero}{\bmath{0}}
\newcommand{\conj}[1]{\overline{#1}}

@@

\section{Least Squares}
Redundant calibration can be achieved by solving the following optimization problem
\begin{equation}
\label{eq:red_least_squares}
\min_{\bz} \|\br\| = \min_{\bz} \|\bd - \bv(\bz)\|, 
\end{equation}
where $\bz = [\bg,\by]^T$. Eq.~\eqref{eq:red_least_squares} is a nonlinear least squares problem.

@@

\citet{Smirnov2015} recently proposed to use this Wirtinger framework instead of the classic real and imaginary approach to perform normal calibration. We will now show
that the Wirtinger framework can also be applied to redundant calibration. Analogous to \cite{Smirnov2015}, we recast Eq.~\eqref{eq:red_least_squares} to 
\begin{equation}
\label{eq:red_least_squares_complex}
\min_{\breve{\bz}} \|\breve{\br}\| = \min_{\breve{\bz}} \|\breve{\bd} - \breve{\bv}(\breve{\bz})\|, 
\end{equation}
where $\breve{\bz} = [\bz,\conj{\bz}]^T$, $\breve{\bd} = [\bd,\conj{\bd}]^T$, $\breve{\bv} = [\bv,\conj{\bv}]$. Eq.~\eqref{eq:red_least_squares_complex} is the augmented counterpart of Eq.~\eqref{eq:red_least_squares}.
If we use the Wirtinger derivative instead of the classic notion of a derivative to define the gradient operator then 
$\bv$ becomes analytic in $\bz$ and $\conj{\bz}$ as a whole. The fact that $\bv$ is now analytic in its argument has the immediate consequence that it becomes possible to use the Gauss-Newton
and the Levenberg-Marquardt algorithm to solve Eq.~\eqref{eq:red_least_squares_complex} \citep{Smirnov2015}.

\subsection{Complex GN and LM}
In this section we discuss how we can use the GN and LM algorithms to solve Eq.~\eqref{eq:red_least_squares_complex} (i.e. estimate $\breve{\bz}$). The complex Jacobian is defined to be
\begin{equation}
\label{eq:Jacobian}
\bJ = \begin{bmatrix}
       \bJ & \bJ^*\\
       \conj{\bJ}^* & \conj{\bJ} 
      \end{bmatrix},
\end{equation}
where 
\begin{align}
\bJ &= \frac{\partial \bv}{\partial \bz}, & \bJ^* &= \frac{\partial \bv}{\partial \conj{\bz}}. 
\end{align}
In Eq.~\eqref{eq:Jacobian}, $\frac{\partial}{\partial \bz}$ and $\frac{\partial}{\partial \conj{\bz}}$ respectively denote the cogradient operator and the conjugate cogradient operator (cite Sorber).
The GN update step is now defined as:
\begin{equation}
 \Delta \breve{\bz} = (\bJ^H\bJ)^{-1}\bJ^H\breve{\br}.
\end{equation}
The LM update rule is very similar, the major difference being a damping factor $\lambda$ is introduced:
\begin{equation}
\Delta \breve{\bz} = (\bJ^H\bJ + \lambda\bD)^{-1}\bJ^H\breve{\br},
\end{equation}
where $\bD=\bI\odot\bJ^H\bJ$. 
NEED TO MENTION THE SILENT INDEX $k$ AND HOW THE UPDATE RULE IS ITERATIVE. ALSO MENTION THAT $\lambda$ IMPROVES THE CONVERGENCE PROPERTIES. WE WILL REFER TO $\bJ^H\bJ$ AS THE 
HESSIAN.

\subsection{Redundant Jacobian and Hessian}
If we apply the definition in Eq.~\eqref{eq:Jacobian} to Eq.~\eqref{eq:red_least_squares_complex} we obtain the following analytic result:
\begin{equation}
\label{eq:Jacobian_red}
\bJ = \begin{bmatrix}
       \bM & \bN\\
       \conj{\bN} & \conj{\bM}
      \end{bmatrix},
\end{equation}
where
\begin{equation}
\bM =\begin{bmatrix}
      \bM_1 & \bM_2
     \end{bmatrix},
\end{equation}
and 
\begin{equation}
\bN = \begin{bmatrix}
       \bN_1 & \bzero
      \end{bmatrix}.
\end{equation}
Moreover,
\begin{align}
\left [ \bM_1 \right ]_{\alpha_{pq},j} &= y_{\phi_{pq}}\conj{g}_q\delta_p^j, & \left [ \bM_2 \right ]_{\alpha_{pq},j} &= g_p\conj{g}_q\delta_{\phi_{pq}}^j 
\end{align}
and
\begin{equation}
\left [ \bN_1 \right ]_{\alpha_{pq},j} = g_py_{\phi_{pq}}\delta^j_q. 
\end{equation}

It is now trivial to compute the Hessian $\bJ^H\bJ$ by using Eq.~\eqref{eq:Jacobian_red}. If we substitute Eq.~\eqref{eq:Jacobian_red} into $\bJ^H\bJ$
we obtain
